The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-07 paper/paper.tex
Make `unfoldPaintingProj` and `unfoldRestrPaintings` equalities definitional (#6)
paper: attempt interval-based notation

The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$. Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency. This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][0,...,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][p-1]$.
Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    \framep[n+1][0,...,p] \arrow[d] \arrow[ddr]\\
    \painting[n][0,...,p-1] \arrow[d, dotted] \\
    \framep[n][0,...,p-1] &
    \restrf[n][0,...,p-1] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
  \end{tikzcd}
\end{center}

In particular, the mutual dependency on one side of $\framep[n][0,...,p-1]$ within the type of $\restrf[n][0,...,p-1]$ and on the other side of $\restrf[n][0,...,p-1]$ within the definition of $\framep[n][0,...,p]$ requires to mutually define the type of $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or $\framep[n][0,...,p]$) as a \emph{function} from $\restrf[n][0,...,p-1]$.

So far, using this recursive definition of  $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$, we are able to specify the three first component of the exected dependent structure:
\begin{align*}
  \framep[n][p]             & : \U                                & \mbox{for all $p\leq n$} \\
  \painting[n][p]           & : \framep[n][p] \rightarrow \U      & \mbox{for all $p\leq n$} \\
  \restrf[n][p]             & : \Pi q \leq n+p.\, \framep[n+1][p]
  \left(\begin{array}{l}
            \framep[n][0,...,p-1]   \\
            \painting[n][0,...,p-1] \\
            \restrf[n][0,...,p-1]   \\
          \end{array}\right)
  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                       \\
\end{align*}
which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][0,...,p]$, $\paintingtype[n][0,...,p]$ and $\restrftype[n][0,...,p]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][0,...,p-1]$ makes it a very dependent function~\citep{Hickey96}:
\begin{align*}
  \framep[n][0,...,p]   & : \frametype[n][0,...,p]                         \\
  \painting[n][0,...,p] & : \paintingtype[n][0,...,p](\framep[n][0,...,p]) \\
  \restrf[n][0,...,p]   & : \restrftype[n][0,...,p]
  \left(\begin{array}{l}
            \framep[n][0,...,p-1]   \\
            \painting[n][0,...,p-1] \\
            \restrf[n][0,...,p-1]   \\
          \end{array}\right)                                            \\
\end{align*}

The type of sequences such as $\restrf[n][0,...,p]$ will be represented by iterated $\Sigma$-types since each $\restrf[n][p]$ may depend on the previous components of the sequence. In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used to represent $\framep[n][0,...,p]$ and $\painting[n][0,...,p]$. Later on, we will write $\framep[n][0,...,p-1]$ for the immediate subsequence of length $p$ of $\framep[n][0,...,p]$ and $\framep[n][p]$ for its last component, and similarly for $\painting[n][0,...,p]$, $\restrf[n][0,...,p]$, etc.

@@

Assuming $\framep[n][0,...,p]$ for $p \leq n$ only requires to define the type of frames, which are just finite products of $\U$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][0,...,p] &  & :      & \U                                   \\
    \frametype[n][]        &  & \defeq & \unittype                            \\
    \frametype[n][0,...,p] &  & \defeq & \frametype[n+1][0,...,p-1] \times \U \\
  \end{array}
\end{equation*}

@@

The types $\paintingtype[n][0,...,p]$ of $\painting[n][0,...,p]$ for $p \leq n$
are type families over frames, so $\framep[n][0,...,p]$ needs to be assumed
beforehand:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & \U                                                                                           \\
    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                    \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

@@

Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$ for $p \leq n+1$, we can
mutually define the types $\restrftype[n][0,...,p-1]$ of frame
restrictions together with $\framep[n+1][0,...p]$ as a function from
$\restrf[n][0,...,p-1]$, introducing also abbreviations for the types
and definitions of layers, as well as for the combination of sequences
of $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and
$\restrf[n][0,...,p-1]$ in one block, which we call
$\depstype[n][0,...p-1]$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \depstype[n][0,..,p-1]          &        & \defeq            &
    \left(\begin{array}{lll}
              \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
              \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
              (\framep[n][0,...,p-1])                                   \\
              \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
              \left(\begin{array}{l}
                  \framep[n][0,...,p-1]   \\
                  \painting[n][0,...,p-1] \\
                \end{array}\right)                             \\
            \end{array}\right)        \\
    \framep[n+1][0,...,p]     &
    \multicolumn{3}{l}{
    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) :\frametype[n+1][0,...,p]}         \\
    \framep[n+1][0,...,0]     &
    \unitpoint                    & \defeq & (\unitpoint,unit)                     \\
    \framep[n+1][0,...,p+1] &
    \deps[n][0,...,p]               & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][0,...,p]
              (\deps[n][0,...,p-1]), \\
              \Sigma d:\framep[n+1][p]
              (\deps[n][0,...,p-1]).
              \, \layer[n][p]
              (\deps[n][0,...,p])
              (d)                    \\
            \end{array}\right)                                              \\
    \restrftype[n][0,...,p-1]       &
    \multicolumn{3}{l}{
    \left(\begin{array}{l}
              \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
              \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
            \end{array}\right) : \U} \\
    \restrftype[n][0,...,0-1]       &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)          & \defeq &
    \unittype                                                                        \\
    \restrftype[n][0,...,(p+1)-1]   &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
            \end{array}\right)        & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n][0,...,p-1]
      :\restrftype[n][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
              \end{array}\right).                     \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]   \\
                \painting[n][0,...,p-1] \\
                \restrf[n][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array}               \\
    \layertype[n][p]                &
    \multicolumn{3}{l}{
      (\deps[n][0,...,p]:\depstype[n][0,...,p])
    : \U}                                                                            \\
    \layertype[n][p]                &
    \deps[n][0,...,p]
                                    & \defeq & \framep[n+1][p]
    (\deps[n][0,...,p-1])
    \rightarrow \U                                                                   \\
    \layer[n][p]                    &
    \multicolumn{3}{l}{
      (\deps[n][0,...,p]:\depstype[n][0,...,p])
      : \layertype[n][p]
      (\deps[n][0,...,p])}
    \\
    \layer[n][p]                    &
    \deps[n][0,...,p]
                                    & \defeq &
    d \mapsto \Pi\omega.\,\painting[n][p](\deps.\restrf[n][p][0][\omega](d))                          \\
  \end{array}
\end{equation*}

@@

Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][p,...,n+1]$, $\painting[n][p,...,n]$, $\framep[n+1][p,...,n+1]$, $\framep[n][p,...,n]$ and $\restrf[n][p,...,n]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][p,...,n+1]$, $\framep[n+1][p,...,n]$ and $\restrf[n][p,...,n]$ respectively depend on the earlier values $\framep[n+1][0,...,p-1]$, $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    & & \painting[n+1][p,...,n+1] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][p,...,n+1]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][0,...,p-1] \arrow[d, dotted] & &
    \painting[n][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][0,...,p-1] &
    \udensdash{\restrf[n][0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][p,...,n] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][p,...,n]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

Let us introduce another abbreviation to combine a full $\deps[n][0,...,n]:\depstype[n][0,...,n]$ with a family $E:\framep[n+1][n+1](\deps[n][0,...,n])\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][0,...,n] & : & \depstype[n][0,...,n]                             \\
            E                   & : & \framep[n+1][n+1](\deps[n][0,...,n]) \rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n+1][p]$ by recursion on $n+1-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][p]      &
    (\fulldeps[n]:\fulldepstype[n])                           \\
    \painting[n+1][n+1]      &
    \fulldeps[n]           & \defeq & \fulldeps.E             \\
    \painting[n+1][p](p\leq n) &
    \fulldeps[n]           & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][0,...,p]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                                 \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

From which we can deduce $\painting[n+1][0,...,p]$ for $p \leq n+1$ by a second recursion, this time on $p$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][0,...,p]         &
    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][0,...,p](\framep[n+1][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
    \painting[n+1][0,...,0-1]       &
    \fulldeps[n]                    & \defeq & \unittype                                                                         \\
    \painting[n+1][0,...,p]         &
    \fulldeps[n]
                                    & \defeq &
    (\painting[n+1][0,...,p-1](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                  \\
  \end{array}
\end{equation*}

TODO: talk about unfoldPaintingProj.

@@

At this stage, we are able to define $\framep[n+1][0,...,n+1]$, $\painting[n+1][0,...,n+1]$ and $\restrftype[n][0,...,n]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$ and $\restrf[n][0,...,n]$, that is from $\deps[n][0,...,n]$. To go further, we need to define the sequence $\restrptype[n][0,...,p-1]$ of types of painting restrictions, for $p \leq n+1$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][0,...,p-1]       &
    (\fulldeps[n]:\fulldepstype[n]) & :      & \U                                                    \\
    \restrptype[n][0,...,0-1]       & E      & \defeq                                    & \unittype \\
    \restrptype[n][0,...,(p+1)-1]   &
    (\fulldeps[n])
                                    & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
    \begin{array}{l}
        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][0,...,p-1]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                  \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                          \\
  \end{array}
\end{equation*}

@@

Thanks to $\restrptype[n][0,...,p-1]$ for $p \leq n+1$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$, $\restrptype[n][0,...,p-1]$ and some $E:\framep[n+1][n+1](\deps[n][0,...,n]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][0,...,p-1]$ as $\depscohstype[n][0,...,p-1]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$. It is also convenient to build $\deps[n+1][0,...,p]$ from $\depscohs[n][0,...,p-1]$, so that we can now build $\framep[n+2][p]$ one step further. Thus, we also include this abbreviation in the definition:

@@

              \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n]               \\

>>>>

The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$. Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency. This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    \framep[n+1][\lbrack 0,p \rbrack] \arrow[d] \arrow[ddr]\\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[\lbrack 0,p-1 \rbrack]$}"', near start, shift right=2mm, hook']\\
  \end{tikzcd}
\end{center}

In particular, the mutual dependency on one side of $\framep[n][\lbrack 0,p-1 \rbrack]$ within the type of $\restrf[n][\lbrack 0,p-1 \rbrack]$ and on the other side of $\restrf[n][\lbrack 0,p-1 \rbrack]$ within the definition of $\framep[n][\lbrack 0,p \rbrack]$ requires to mutually define the type of $\restrf[n][\lbrack 0,p-1 \rbrack]$ together with $\framep[n][p]$ (or $\framep[n][\lbrack 0,p \rbrack]$) as a \emph{function} from $\restrf[n][\lbrack 0,p-1 \rbrack]$.

So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
\begin{align*}
  \framep[n][p]             & : \U                                & \mbox{for all $p\leq n$} \\
  \painting[n][p]           & : \framep[n][p] \rightarrow \U      & \mbox{for all $p\leq n$} \\
  \restrf[n][p]             & : \Pi q \leq n+p.\, \framep[n+1][p]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)
  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                       \\
\end{align*}
which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
\begin{align*}
  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)                                                                    \\
\end{align*}

The type of sequences such as $\restrf[n][\lbrack 0,p \rbrack]$ will be represented by iterated $\Sigma$-types since each $\restrf[n][p]$ may depend on the previous components of the sequence. In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used to represent $\framep[n][\lbrack 0,p \rbrack]$ and $\painting[n][\lbrack 0,p \rbrack]$. Later on, we will write $\framep[n][\lbrack 0,p-1 \rbrack]$ for the immediate subsequence of length $p$ of $\framep[n][\lbrack 0,p \rbrack]$ and $\framep[n][p]$ for its last component, and similarly for $\painting[n][\lbrack 0,p \rbrack]$, $\restrf[n][\lbrack 0,p \rbrack]$, etc.

@@

Assuming $\framep[n][\lbrack 0,p \rbrack]$ for $p \leq n$ only requires to define the type of frames, which are just finite products of $\U$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][\lbrack 0,p \rbrack] &  & :      & \U                                               \\
    \frametype[n][]                    &  & \defeq & \unittype                                        \\
    \frametype[n][\lbrack 0,p \rbrack] &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
  \end{array}
\end{equation*}

@@

The types $\paintingtype[n][\lbrack 0,p \rbrack]$ of $\painting[n][\lbrack 0,p \rbrack]$ for $p \leq n$
are type families over frames, so $\framep[n][\lbrack 0,p \rbrack]$ needs to be assumed
beforehand:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \paintingtype[n][\lbrack 0,p \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p \rbrack]) & :      & \U                                                                                                                   \\
    \paintingtype[n][]                    & \unitpoint                                                           & \defeq & \unittype                                                                                                            \\
    \paintingtype[n][\lbrack 0,p \rbrack] & (\framep[n][\lbrack 0,p \rbrack])                                    & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

@@

Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can
mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame
restrictions together with $\framep[n+1][0,...p]$ as a function from
$\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types
and definitions of layers, as well as for the combination of sequences
of $\framep[n][0,..,p-1]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
$\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
$\depstype[n][0,...p-1]$:
    \depstype[n][0,..,p-1]                    &        & \defeq            &
              \framep[n][\lbrack 0,p-1 \rbrack]   & : & \frametype[n][\lbrack 0,p-1 \rbrack]    \\
              \painting[n][\lbrack 0,p-1 \rbrack] & : & \paintingtype[n][\lbrack 0,p-1 \rbrack]
              (\framep[n][\lbrack 0,p-1 \rbrack])                                               \\
              \restrf[n][\lbrack 0,p-1 \rbrack]   & : & \restrftype[n][\lbrack 0,p-1 \rbrack]
                  \framep[n][\lbrack 0,p-1 \rbrack]   \\
                  \painting[n][\lbrack 0,p-1 \rbrack] \\
    \framep[n+1][\lbrack 0,p \rbrack]         &
    (\deps[n][\lbrack 0,p-1 \rbrack]:\depstype[n][\lbrack 0,p-1 \rbrack]) :\frametype[n+1][\lbrack 0,p \rbrack]}         \\
    \framep[n+1][\lbrack 0,0 \rbrack]         &
    \unitpoint                                & \defeq & (\unitpoint,unit)                                               \\
    \framep[n+1][\lbrack 0,p+1 \rbrack]       &
    \deps[n][\lbrack 0,p \rbrack]             & \defeq &
              \framep[n+1][\lbrack 0,p \rbrack]
              (\deps[n][\lbrack 0,p-1 \rbrack]), \\
              \Sigma d:\framep[n+1][p]
              (\deps[n][\lbrack 0,p-1 \rbrack]).
              \, \layer[n][p]
              (\deps[n][\lbrack 0,p \rbrack])
              (d)                                \\
    \restrftype[n][\lbrack 0,p-1 \rbrack]     &
              \framep[n][\lbrack 0,p-1 \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]                                         \\
              \painting[n][\lbrack 0,p-1 \rbrack]:\paintingtype[n][\lbrack 0,p-1 \rbrack](\framep[n][\lbrack 0,p-1 \rbrack]) \\
            \end{array}\right) : \U} \\
    \restrftype[n][\lbrack 0,0-1 \rbrack]     &
    \restrftype[n][\lbrack 0,(p+1)-1 \rbrack] &
              \framep[n][\lbrack 0,p \rbrack]   \\
              \painting[n][\lbrack 0,p \rbrack] \\
      \Sigma \restrf[n][\lbrack 0,p-1 \rbrack]
      :\restrftype[n][\lbrack 0,p-1 \rbrack]
                \framep[n+1][\lbrack 0,p-1 \rbrack]   \\
                \painting[n+1][\lbrack 0,p-1 \rbrack] \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
                \framep[n][\lbrack 0,p-1 \rbrack]   \\
                \painting[n][\lbrack 0,p-1 \rbrack] \\
                \restrf[n][\lbrack 0,p-1 \rbrack]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \layertype[n][p]                          &
      (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
    \layertype[n][p]                          &
    \deps[n][\lbrack 0,p \rbrack]
                                              & \defeq & \framep[n+1][p]
    (\deps[n][\lbrack 0,p-1 \rbrack])
    \rightarrow \U                                                                                                       \\
    \layer[n][p]                              &
      (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
      : \layertype[n][p]
      (\deps[n][\lbrack 0,p \rbrack])}
    \layer[n][p]                              &
    \deps[n][\lbrack 0,p \rbrack]
    d \mapsto \Pi\omega.\,\painting[n][p](\deps.\restrf[n][p][0][\omega](d))                                             \\

@@

Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    & & \painting[n+1][\lbrack p,n+1 \rbrack] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][\lbrack 0,p-1 \rbrack]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][\lbrack p,n+1 \rbrack]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] & &
    \painting[n][\lbrack p,n-1 \rbrack] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \udensdash{\restrf[n][\lbrack 0,p-1 \rbrack]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][\lbrack p,n \rbrack] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][\lbrack p,n \rbrack]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

Let us introduce another abbreviation to combine a full $\deps[n][\lbrack 0,n \rbrack]:\depstype[n][\lbrack 0,n \rbrack]$ with a family $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][\lbrack 0,n \rbrack] & : & \depstype[n][\lbrack 0,n \rbrack]                               \\
            E                             & : & \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n+1][p]$ by recursion on $n+1-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][p]          &
    (\fulldeps[n]:\fulldepstype[n])                                       \\
    \painting[n+1][n+1]        &
    \fulldeps[n]               & \defeq & \fulldeps.E                     \\
    \painting[n+1][p](p\leq n) &
    \fulldeps[n]               & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

From which we can deduce $\painting[n+1][\lbrack 0,p \rbrack]$ for $p \leq n+1$ by a second recursion, this time on $p$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][\lbrack 0,p \rbrack]   &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p \rbrack](\framep[n+1][\lbrack 0,p \rbrack](\fulldeps.\deps[n-1][\lbrack 0,p \rbrack])) \\
    \painting[n+1][\lbrack 0,0-1 \rbrack] &
    \fulldeps[n]                          & \defeq & \unittype                                                                                                             \\
    \painting[n+1][\lbrack 0,p \rbrack]   &
    \fulldeps[n]
                                          & \defeq &
    (\painting[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                                                \\
  \end{array}
\end{equation*}

@@

At this stage, we are able to define $\framep[n+1][\lbrack 0,n+1 \rbrack]$, $\painting[n+1][\lbrack 0,n+1 \rbrack]$ and $\restrftype[n][\lbrack 0,n \rbrack]$ from $\framep[n][\lbrack 0,n \rbrack]$, $\painting[n][\lbrack 0,n \rbrack]$ and $\restrf[n][\lbrack 0,n \rbrack]$, that is from $\deps[n][\lbrack 0,n \rbrack]$. To go further, we need to define the sequence $\restrptype[n][\lbrack 0,p-1 \rbrack]$ of types of painting restrictions, for $p \leq n+1$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack]     &
    (\fulldeps[n]:\fulldepstype[n])           & :      & \U                                                                \\
    \restrptype[n][\lbrack 0,0-1 \rbrack]     & E      & \defeq                                                & \unittype \\
    \restrptype[n][\lbrack 0,(p+1)-1 \rbrack] &
    (\fulldeps[n])
                                              & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
    \begin{array}{l}
        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                              \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                                \\
  \end{array}
\end{equation*}

@@

Thanks to $\restrptype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can mutually define $\restrf[n+1][\lbrack 0,p \rbrack]$ and $\cohftype[n][\lbrack 0,p-1 \rbrack]$ from $\framep[n][\lbrack 0,n \rbrack]$, $\painting[n][\lbrack 0,n \rbrack]$, $\restrf[n][\lbrack 0,n \rbrack]$, $\restrptype[n][\lbrack 0,p-1 \rbrack]$ and some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][\lbrack 0,p-1 \rbrack]$ as $\depscohstype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$. It is also convenient to build $\deps[n+1][\lbrack 0,p \rbrack]$ from $\depscohs[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+2][p]$ one step further. Thus, we also include this abbreviation in the definition:

@@

              \fulldeps[n][\lbrack 0,n \rbrack] & : & \fulldepstype[n][\lbrack 0,n \rbrack]               \\
